Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-19 ms.tex
various edits

Where $Y_{l}^{m}$ are the real spherical harmonics, and the $a_{lm}$ are their 
corresponding real coefficients. The angle $\phi_p$ is taken simply to be 
$l_{gal, p}$ and $\theta_p$=$(90^{\circ}-b_{gal, p})$. Thus, we have replaced 
the Solar dipole term with a sum of 24 spherical harmonic templates, which, 
when multiplied by the best-fit $a_{lm}$ coefficients and subtracted from 
\PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
linear. Figure \ref{fig:harm} illustrates the improved correlation of 100 GHz 
vs. 857 GHz when including the spherical harmonic corrections relative to the 
dipole-only correction. The spherical harmonic decomposition of Equation 
\ref{equ:harm} did not improve the correlations at higher frequencies 
sufficiently to warrant replacing the dipole-only correction in those cases.

@@

% also might be worth mentioning that the MCMC analysis involves constraints
% where the zero level matters, whereas the correlation slope analysis here
% renders the zero levels irrelevant

@@

% scatterplot figure showing linear regression of EBV vs. tau
\begin{figure}
\begin{center}
\epsfig{file=calib_ebv.eps, width=3.3in}
\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
$\tau_{545}$.}
\end{center}
\end{figure}

@@

% need to explain SSPP acronym somewhere ?
% cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?

@@

\section{Data Release}
\label{sec:release}
We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
summarizing the results of of our two-component dust fits.

@@

%at some point in this should make statements re: the fact that in terms
%of predicting *emission* the conversion to tau is unnecessary and
%and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity

>>>>

Where $Y_{l}^{m}$ are the real spherical harmonics, and the $a_{lm}$ are their 
corresponding real coefficients. The angle $\phi_p$ is taken simply to be 
$l_{gal, p}$ and $\theta_p$=$(90^{\circ}-b_{gal, p})$. Thus, we have replaced 
the Solar dipole term with a sum of 24 spherical harmonic templates, which, 
when multiplied by the best-fit $a_{lm}$ coefficients and subtracted from 
\PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
linear. Figure \ref{fig:harm} illustrates the improved correlation of 100 GHz 
vs. 857 GHz when including the spherical harmonic corrections relative to the 
dipole-only correction. The spherical harmonic decomposition of Equation 
\ref{equ:harm} did not improve the correlations at higher frequencies 
enough to warrant replacing the dipole-only correction in those cases.

@@

@@

\begin{figure}
\begin{center}
\epsfig{file=calib_ebv.eps, width=3.3in}
\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
$\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$ and 
$|\beta|$$>$20$^{\circ}$.}
\end{center}
\end{figure}

@@

@@

\section{Data Release}
\label{sec:release}
We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
summarizing the results of our full-resolution two-component dust fits. 
Refer to the data release documentation and FITS file headers for further 
details.

% will we release software for making thermal dust predictions (i suppose
% we can just release a reddening map, and there doesn't need to be 
% any software released in that regard?)

@@
